Drug Toxicity as the Leading Cause of Homeless Deaths in Toronto

### 2024-09-27 paper/paper.qmd
Update paper.qmd

```{r}
#| include: false
#| warning: false
#| message: false
library(here)
library(tidyverse)
library(opendatatoronto)
library(knitr)
library(readr)
cleaned_death_by_month_data <- read_csv("~/sta304/starter_folder-main/data/analysis_data/analysis_death_by_month_data.csv")
cleaned_death_by_cause_data <- read_csv("~/sta304/starter_folder-main/data/analysis_data/analysis_death_by_cause_data.csv")
death_by_cause_data <- read_csv("~/sta304/starter_folder-main/data/analysis_data/death_by_cause_data.csv")
combined_deaths <- read_csv("~/sta304/starter_folder-main/data/analysis_data/deaths_over_time.csv")
```

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
library(here)
library(tidyverse)
library(opendatatoronto)
library(knitr)
library(readr)
cleaned_death_by_month_data <- read_csv("~/sta304/starter_folder-main/data/analysis_data/analysis_death_by_month_data.csv")
cleaned_death_by_cause_data <- read_csv("~/sta304/starter_folder-main/data/analysis_data/analysis_death_by_cause_data.csv")
combined_deaths <- read_csv("~/sta304/starter_folder-main/data/analysis_data/deaths_over_time.csv")
```
